Correlating Scanning Ion Conductance and Super-Resolved Fluorescence Microscopy

### 2020-09-04 manuscript.tex
First draft of abstract (still too long)

\author{Name of First Author and Name of Second Author}
% Use \authorrunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long

\institute{%
  Name of First Author \and
  Name of Second Author \and
  Patrick Happel \at
  Nanoscopy Group,
  RUBION, Ruhr-Universität Bochum,
  Universtätsstraße 150, D-44801 Bochum, Germany
  \email{patrick.happel@rub.de}
}

@@

\abstract{%
sdfa  
}

>>>>

\author{Annika Haak, Astrid Gesper and Patrick Happel}
\authorrunning{Haak et al.}
% Use \authorrunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long

\institute{%
  Annika Haak\and
  Astrid Gesper \and
  Patrick Happel \at
  Nanoscopy Group,
  RUBION, Ruhr-Universität Bochum,
  Universtätsstraße 150, D-44801 Bochum, Germany
  \email{patrick.happel@rub.de}
}

@@

\abstract{%
  The development of diffraction unlimited fluorescence microscopy has paved
  the way for a detailed understanding of cellular dynamics since live-cell
  investigations with a resolution below 100\,nm have become
  available, allowing to investigate 
  labeled specimen such as proteins and their distribution within a cell at a
  new level of detail. However, the place of the interaction between the
  cell's internal processes and external signals, the cell membrane, cannot be
  investigated by fluorescence microscopy since inserting fluorescent dyes
  alters the physico-chemical properties of the cell membrane.
%
  The latter, however, is a unique strength of scanning ion conductance
  microscopes (SICM),
  which use a fine tip to determine the topography of the investigated sample
  and thus allow to investigate the cell membrane without labelling.    
%  
  Since both types of microscopes can be applied to living cells and provide a
  resolution below the diffraction limit, correlating data from the two
  seems a promising approach to further the understanding of
  the organisation of the cell plasma membrane and of the mechanisms involved
  in the transport processes across it.
%  
  Here we briefly introduce the different approaches to Super-Resolved
  Fluorescence Microscopy (SRFM) and review the applications of correlating SICM
  and diffraction-limited as well as diffraction-unlimited fluorescence
  microscopy. Lastly, we discuss potential implementations of combined
  SRFM/SICM instruments and the potential pitfalls that may arise during the
  development of such, hitherto putative, instruments.
}
